A Wait-free Queue with Polylogarithmic Step Complexity

### 2023-04-01 podc_paper/podc-submission.tex
added abstract that was deleted by mistake
Minor edits; fixed amortized complexity bound for GC
started reformatting for camera-ready

%%
%% This is file generated with the docstrip utility from the source file: 
%%
%% samples.dtx  (with options: `acmsmall-conf')
%% With some modifications for PODC 2023.
%% For the copyright see the source file.
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[acmsmall,nonacm,anonymous]{acmart}

@@

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

@@

\author{Hossein Naderibeni}
\email{hnaderi268@gmail.com}
\affiliation{%
  \institution{York University}
  \streetaddress{P.O. Box 1212}
  \city{Toronto}
  \state{Ontario}
  \country{Canada}
  \postcode{43017-6221}
}
\author{Eric Ruppert}
\affiliation{%
  \institution{York University}
  \streetaddress{P.O. Box 1212}
  \city{Toronto}
  \state{Ontario}
  \country{Canada}
  \postcode{43017-6221}
}
\email{ruppert@cse.yorku.ca}
\orcid{0000-0001-5613-8701}

\settopmatter{printacmref=false}  % REMOVE THIS LINE FOR CAMERA READY

\begin{abstract}
We present a novel linearizable wait-free queue implementation using single-word 
CAS instructions.
Previous lock-free queue implementations from \op{CAS} all have amortized step complexity of $\Omega(p)$ per operation in worst-case executions, 
where $p$ is the number of processes that access the queue.
Our new wait-free queue  takes $O(\log p)$ steps per enqueue and $O(\log^2 p +\log q)$ steps per dequeue, where $q$ is the size of the queue.
A bounded-space version of the implementation has amortized step complexity of $O(\log^2 p +\log q)$ per operation.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
%\keywords{concurrent data structures, wait-free queues}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

%OMIT IN SUBMISSION FOR ANONYMITY
%\paragraph{Acknowledgements}
%We thank Franck van Breugel for his helpful comments.
%Funding was provided by the Natural Sciences and Engineering Research Council of Canada.

\newpage

@@

\newpage
\appendix

\input{correctness-details}

\input{algorithm-GC}

\input{correctness-GC}

>>>>

%%
%% This is file generated with the docstrip utility from the source file: 
%%
%% samples.dtx  (with options: `acmsmall-conf')
%% With some modifications for PODC 2023.
%% For the copyright see the source file.
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{acmart}
%\documentclass[acmsmall,nonacm]{acmart}

@@

%%
%% end of the preamble, start of the body of the document source.

@@

\author{Hossein Naderibeni}
%\email{hnaderi268@gmail.com}
\affiliation{%
  \institution{York University}
  \streetaddress{P.O. Box 1212}
  \city{Toronto}
  \state{Ontario}
  \country{Canada}
  \postcode{43017-6221}
}
\author{Eric Ruppert}
\affiliation{%
  \institution{York University}
  \streetaddress{P.O. Box 1212}
  \city{Toronto}
  \state{Ontario}
  \country{Canada}
  \postcode{43017-6221}
}
%\email{ruppert@cse.yorku.ca}
\orcid{0000-0001-5613-8701}

%\settopmatter{printacmref=false}  % REMOVE THIS LINE FOR CAMERA READY
\copyrightyear{2023}
\acmYear{2023}
\setcopyright{acmlicensed}\acmConference[PODC '23]{xxx}{xxx}{xxx}
\acmBooktitle{xxx}
\acmPrice{xxx}
\acmDOI{xxx}
\acmISBN{xxx}
\settopmatter{printacmref=true}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003809.10010031</concept_id>
<concept_desc>Theory of computation~Data structures design and analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003809.10011778</concept_id>
<concept_desc>Theory of computation~Concurrent algorithms</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Data structures design and analysis}
\ccsdesc[500]{Theory of computation~Concurrent algorithms}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.

\keywords{concurrent data structures, wait-free queues}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.

\begin{document}

\begin{abstract}
We present a novel linearizable wait-free queue implementation using single-word CAS instructions.  
Previous lock-free queue implementations from \op{CAS} all have amortized step complexity of 
$\Omega(p)$ per operation in worst-case executions, where $p$ is the number of processes that 
access the queue.  Our new wait-free queue  takes $O(\log p)$ steps per enqueue and 
$O(\log^2 p +\log q)$ steps per dequeue, where $q$ is the size of the queue.  
A bounded-space version of the implementation has $O(\log p \log(p+q))$ amortized step complexity  per operation.
\end{abstract}

\maketitle

\Eric{Remove references to appendix and replace with tech report}

@@

\paragraph{Acknowledgements}
We thank Franck van Breugel and the anonymous referees for their helpful comments.
Funding was provided by the Natural Sciences and Engineering Research Council of Canada.

@@

%\appendix
%\input{correctness-details}
%\input{algorithm-GC}
%\input{correctness-GC}
